\documentclass[letterpaper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.25in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\normalsize
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r} % Changed 0.97\textwidth to \textwidth
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}
% \renewcommand{\labelitemi}{$\circ$}
\renewcommand{\labelitemii}{$\circ$}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}


\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = black, %Colour for external hyperlinks
  linkcolor    = black, %Colour of internal links
  citecolor   = red %Colour of citations
}


\begin{document}


%----------HEADING-----------------
\begin{center}
    \textbf{\Large ROHITH PAVULURU} \\ \vspace{2pt}
    \small
    \href{mailto:pavuluru.rohith@gmail.com}{pavuluru.rohith@gmail.com} $|$ 
    \href{https://linkedin.com/in/pavuluru-rohith}{linkedin.com/in/pavuluru-rohith} $|$
    \href{https://github.com/Pavulururohith}{github.com/Pavulururohith} $|$
    \href{https://rohith-pavuluru-portfolio.vercel.app}{rohith-pavuluru-portfolio.vercel.app} $|$ 
    \href{tel:+19303334291}{+19303334291}
\end{center}
\vspace{-10pt}

%-----------EXECUTIVE PROFILE-----------------
\section{PROFESSIONAL SUMMARY}
% \resumeSubHeadingListStart
    \small{\textbf{Software Engineer} with experience in \textbf{scalable system design, full-stack development}, and \textbf{performance optimization}. Specializing in \textbf{Python, Java, JavaScript}, and \textbf{cloud infrastructure}, I build \textbf{robust, user-focused solutions} from low-level systems to customer-facing UIs. Proven track record in \textbf{collaborative development workflows} with demonstrated success in \textbf{code quality} and \textbf{system maintainability}.}
% \resumeSubHeadingListEnd
\vspace{-2pt}

%-----------TECHNICAL EXPERTISE-----------------
\section{TECHNICAL EXPERTISE}
\resumeSubHeadingListStart
\resumeSubItem{}{\small\textbf{Programming Languages:} Python, Java, JavaScript, C, C++, Go, SQL.}
\resumeSubItem{}{\small\textbf{Web Development:} React, Node.js, Django, HTML5, CSS3, Next.js, RESTful APIs.}
\resumeSubItem{}{\small\textbf{Cloud \& Infrastructure:} AWS (Lambda, S3, IoT Core), Docker, Kubernetes, CI/CD, Git.}
\resumeSubItem{}{\small\textbf{Databases \& Systems:} MySQL, MongoDB, Snowflake, distributed systems, performance optimization.}
\resumeSubItem{}{\small\textbf{Development Tools:} Git, Jenkins, GitHub Actions, Postman, Linux, Firebase, Agile methodologies.}
\resumeSubItem{}{\small\textbf{AI \& Data Processing:} Machine Learning (ML), PyTorch, scikit-learn, data pipelines, real-time processing.}
\resumeSubHeadingListEnd
\vspace{-3pt}

%-----------EDUCATION AND CERTIFICATIONS-----------------
\section{EDUCATION}
% \resumeSubHeadingListStart
\small{\textbf{Master of Science in Computer Science} $|$ Indiana University Bloomington $|$ GPA: 3.97 $|$ May 2025}\\
\small{Coursework: Applied Algorithms, Software Engineering, Machine Learning (ML), Big Data Applications}\\
% \vspace{-5pt}
\small{\textbf{Bachelor of Engineering} $|$ BMS Institute of Technology and Management $|$ CGPA: 9.11 $|$ May 2023}
% \vspace{-5pt}\
% \resumeSubHeadingListEnd
\vspace{-1pt}


%-----------PROFESSIONAL EXPERIENCE-----------------
\section{PROFESSIONAL EXPERIENCE}
\resumeSubHeadingListStart
\vspace{-5pt}
\resumeSubheading
  {Indiana University Bloomington}{Bloomington, United States}
  {Software Engineer}{January 2025 - July 2025}
  \resumeItemListStart
    \resumeItem {} {Built \textbf{scalable Smart Feedback System} using \textbf{AWS cloud services} for automated quiz generation with \textbf{intuitive UI/UX design}, achieving \textbf{3x improvement in qualitative feedback} generation.}
    \resumeItem {} {Developed \textbf{drag-and-drop and image grouping functionalities} using modern \textbf{JavaScript frameworks}, generating 1,000+ unique interpretations for enhanced data analysis.}
    \resumeItem {} {Designed \textbf{performance-optimized UI components} ensuring efficient data collection processes for both research and production environments.}
  \resumeItemListEnd
  
\resumeSubheading
  {Nokia Solutions and Networks}{Bengaluru, India}
  {DevOps Engineer}{February 2023 - July 2023}
  \vspace{-1.5pt}
  \resumeItemListStart
    \resumeItem {} {Engineered \textbf{large-scale monitoring solutions} using \textbf{Kafka} and \textbf{Grafana}, improving \textbf{system reliability by 22\%} and optimizing incident response workflows.}
    \resumeItem {} {Built \textbf{CI/CD pipelines} with \textbf{Kubernetes} and \textbf{Docker}, accelerating deployments by \textbf{25\%} while achieving \textbf{50\% reduction in image sizes} through optimization techniques.}
    \resumeItem {} {Maintained \textbf{92.4\% code coverage} through rigorous testing frameworks, ensuring robust and maintainable software deployments.}
  \resumeItemListEnd
% \vspace{-1pt}
\resumeSubheading
  {Nano Robotics Embed Technologies}{Bengaluru, India}
  {Software Engineer}{July 2022 - October 2022}
\vspace{-1.5pt}
  \resumeItemListStart
    \resumeItem {} {Developed \textbf{machine learning models} using \textbf{AWS services} (IoT Core, Lambda, S3, SageMaker), boosting forecasting \textbf{accuracy by 12\%} while processing \textbf{1M+ data points}.}
    \resumeItem {} {Built \textbf{real-time alert system} with \textbf{API integration} (Twilio), creating automated notifications that enhanced public safety across 10km radius coverage.}
  \resumeItemListEnd
\vspace{-1pt}
\resumeSubheading
{Pramahasoft Solutions Pvt Ltd}{Hyderabad, India}
  {Software Engineer}{February 2021 - June 2022}
  \resumeItemListStart
    \resumeItem {} {Architected \textbf{scalable data pipelines} processing \textbf{200,000+ transactions hourly} with \textbf{98.92\% accuracy}, implementing \textbf{real-time streaming} and automated workflows.}
    \resumeItem {} {Built \textbf{centralized reporting infrastructure} accelerating report generation by \textbf{40\%} while handling \textbf{2x larger datasets}, demonstrating expertise in performance optimization.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-1pt}

%-----------ACADEMIC PROJECTS-----------------
\section{ACADEMIC PROJECTS}
\resumeSubHeadingListStart
\vspace{-5pt}

\resumeSubItem{}{\textbf{\href{https://github.com/nihalshetty-boop/P565-SP24-LMS-G21-Backend}{CourseCraft - Learning Management System}}}
\vspace{-1pt}
\resumeItemListStart
    \resumeItem {} {Engineered \textbf{full-stack LMS} with \textbf{Firebase} and \textbf{AWS}, implementing \textbf{multi-factor authentication} and role-based access control for enhanced security.}
    \resumeItem {} {Collaborated in \textbf{Agile development team}, delivering scalable educational platform with differentiated dashboards and diverse assignment management capabilities.}
\resumeItemListEnd
% \vspace{-5pt}
\resumeSubItem{}{\textbf{\href{https://github.com/Pavulururohith/Smart-Form}{Smart Form - NLP Duplicate Detection}}}
\resumeItemListStart
    \resumeItem {} {Built \textbf{Django application} with \textbf{NLP algorithms} achieving \textbf{95\% accuracy} in duplicate detection, reducing project selection time by \textbf{40\%} across 5 university departments.}
    \resumeItem {} {Deployed to \textbf{1,000+ users} with \textbf{4.8/5 user satisfaction score}, demonstrating expertise in user-focused design and scalable system deployment.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\end{document}


